Sketch Recognition and Understanding

### 2009-08-04 trunk/draft/System.tex

@@

>>>>

Let $x_i$ , $i$ = $1.2 \dots,N$ , be the feature vectors of the training set, $X$ . These
belong to either of two classes that are linearly spereable $\omega_1=1$ and  $\omega_2=-1$.
The goal, is to design a hyperplane which solve the equation 
\begin{equation}
g(x) = \omega^{T} x + \omega g = 0
\label{eq:svmhyper}
\end{equation}
 % Vladimir N. Vapnik. Statistical Learning Theory. John Wiley & Sons, Inc., New
% York, NY, September 1998.

@@

\section{Step by Step Example}
\label{secstepExample}
In this section a step by step example is presented to clearify the presented sytesm. Let us make an assumption that the user will draw a clock using two strokes. Figure \ref{} show the two stroke and how the user draw them. The next steps demonstrate how ouput of the system after each step

\begin{landscape}
\begin{scriptsize}

%\begin{table}
	%\centering

%\scalebox{0.6}{		
\begin{longtable}{|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{13cm}|}
	\caption{StepsStroke1}
	\label{tab:StepsStroke1} \\

\hline 
\multicolumn{1}{|p{2cm}|}{\textbf{Step}} & 
\multicolumn{1}{p{2cm}|}{\textbf{Discription}} &
 \multicolumn{1}{p{2cm}|}{\textbf{Inputs}} &
 \multicolumn{1}{p{2cm}|}{\textbf{Details}} &
 \multicolumn{1}{p{13cm}|}{\textbf{Output}} 
\\ \hline 
\endfirsthead

\hline
\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\multicolumn{1}{|p{2cm}|}{\textbf{Step}} & 
\multicolumn{1}{p{2cm}|}{\textbf{Discription}} &
 \multicolumn{1}{p{2cm}|}{\textbf{Inputs}} &
 \multicolumn{1}{p{2cm}|}{\textbf{Details}} &
 \multicolumn{1}{p{13cm}|}{\textbf{Output}} 
\\ \hline 
\endhead

%Step & Discription of Step & Input & Steps & Output \\ \hline
Stroke 1 & Extracting point and computing boundary data & -- &  see Section \ref{sec:Preprocessing} & 
\begin{scriptsize}
Stroke has 62 points = [P(198.0,153.0), P(197.0,150.0), P(197.0,145.0), P(198.0,140.0), P(203.0,125.0), P(205.0,120.0) , P(205.0,117.0), P(210.0,111.0) , P(214.0,103.0) , P(219.0,97.0), P(225.0,89.0) , P(229.0,85.0) , P(242.0,77.0) , P(247.0,73.0) , P(275.0,64.0) , P(287.0,62.0) , P(325.0,62.0) , P(333.0,63.0) , P(362.0,68.0) , P(372.0,72.0) , P(391.0,77.0) , P(406.0,83.0) , P(424.0,91.0) , P(440.0,100.0), P(474.0,133.0) , P(485.0,149.0) , P(492.0,164.0) , P(499.0,182.0) , P(501.0,191.0) , P(501.0,207.0) , P(499.0,222.0) , P(496.0,239.0) , P(471.0,292.0) , P(467.0,302.0) , P(456.0,315.0) , P(441.0,329.0) , P(427.0,339.0) , P(418.0,344.0) , P(398.0,354.0) , P(336.0,371.0) , P(283.0,376.0) , P(263.0,378.0) , P(242.0,378.0) , P(232.0,376.0) , P(213.0,373.0) , P(194.0,367.0) , P(177.0,362.0) , P(138.0,343.0) , P(129.0,336.0) , P(124.0,331.0) , P(120.0,321.0) , P(115.0,310.0) , P(113.0,297.0) , P(112.0,284.0) , P(114.0,256.0) , P(121.0,219.0) , P(128.0,202.0) , P(137.0,184.0) , P(143.0,172.0) , P(154.0,161.0) , P(172.0,146.0) , P(172.0,146.0)]

 Bonding box is  = Corner P(112.0, 62.0), w= 389.0, h=  316.0
 number of point in this stroke is   62
\end{scriptsize}
 \\ \hline
Possible Dominate point Extraction & Computing and for details see Section\ref{sec:Preprocessing} &  Stroke points  & 1. compute   the pdp  &    Number of $P_{dp}$  = 11
 Pdp = [ 2 (197.0 , 145.0 ), 4 (203.0 , 125.0 ), 3 (198.0 , 140.0 ), 22 (424.0 , 91.0 ), 19 (372.0 , 72.0 ), 26 (492.0 , 164.0 ), 28 (501.0 , 191.0 ), 9 (219.0 , 97.0 ), 31 (496.0 , 239.0 ), 0 (198.0 , 153.0 ), 41 (263.0 , 378.0 )]

\\ \hline 
Segmentation & Segmentation of Ellipse & $P_{dp}$   &  Ellipse fitting  & 
 Segmented as Ellipse with dimensions  a = 194.5 ,b = 194.5 , Center( 306.5,  220.0 )   with Error =  2.276869953758031 , Percent =0.9093857875960022
 certainty  =  0.1997008626019765 
\\ \hline

Stroke 2 & Extracting point and computing boundary data & -- &  see Section \ref{sec:Preprocessing} &
\begin{scriptsize}
Stroke has 205 points = [P(201.0,179.0) , P(202.0,180.0) , P(202.0,182.0) , P(202.0,185.0) , P(202.0,187.0) , P(202.0,190.0) , P(202.0,192.0) , P(202.0,196.0) , P(202.0,202.0) , P(201.0,206.0) , P(200.0,219.0) , P(198.0,231.0) , P(198.0,234.0) , P(198.0,238.0) , P(197.0,244.0) , P(197.0,248.0) , P(197.0,251.0) , P(196.0,258.0) , %P(196.0,260.0) , P(196.0,263.0) , P(195.0,265.0) , P(195.0,266.0) , P(195.0,269.0) , P(195.0,271.0) , P(195.0,273.0) , P(195.0,278.0) , P(195.0,279.0) , P(195.0,281.0) , P(195.0,282.0) , P(195.0,284.0) , P(195.0,285.0) , P(195.0,288.0) , P(195.0,290.0) , P(195.0,295.0) , P(195.0,297.0) , P(195.0,298.0) , P(196.0,298.0) , P(196.0,299.0) , P(196.0,300.0) , P(196.0,301.0) , P(197.0,301.0) , P(198.0,301.0) , P(200.0,301.0) , P(203.0,301.0) , %P(206.0,301.0) , P(208.0,301.0) , P(213.0,301.0) , P(217.0,302.0) , P(219.0,302.0) , P(223.0,303.0) , P(234.0,304.0) , P(237.0,304.0) , P(240.0,306.0) , P(246.0,306.0) , P(247.0,307.0) , P(248.0,307.0) , P(249.0,307.0) , P(250.0,307.0) , P(250.0,306.0) , P(250.0,305.0) , P(250.0,304.0) , P(250.0,302.0) , P(251.0,299.0) , P(251.0,296.0) , P(251.0,294.0) , P(251.0,289.0) , P(252.0,285.0) , P(253.0,279.0) , P(253.0,274.0) , P(253.0,271.0) , P(253.0,264.0) , P(253.0,257.0) , P(254.0,252.0) , P(254.0,241.0) , P(254.0,237.0) , P(255.0,232.0) , P(255.0,229.0) , P(255.0,225.0) , P(256.0,212.0) , P(256.0,209.0) , P(256.0,206.0) , P(257.0,205.0) , P(257.0,200.0) , P(257.0,197.0) , P(258.0,195.0) , P(258.0,194.0) , P(258.0,189.0) , P(258.0,187.0) , P(258.0,186.0) , P(259.0,184.0) , P(259.0,181.0) , P(259.0,179.0) , P(259.0,178.0) , P(260.0,176.0) , P(260.0,174.0) , P(260.0,173.0) , P(260.0,172.0) , P(260.0,171.0) , P(260.0,169.0) , P(260.0,168.0) , P(260.0,167.0) , P(261.0,166.0) , P(261.0,165.0) , P(261.0,164.0) , P(261.0,162.0) , P(262.0,162.0) , P(263.0,162.0) , P(264.0,162.0) , P(268.0,162.0) , P(275.0,162.0) , P(279.0,162.0) , P(289.0,162.0) , P(291.0,162.0) , P(301.0,163.0) , P(305.0,164.0) , P(312.0,164.0) , P(315.0,165.0) , P(318.0,165.0) , P(319.0,165.0) , P(319.0,166.0) , P(320.0,168.0) , P(320.0,171.0) , P(320.0,173.0) , P(320.0,176.0) , P(321.0,182.0) , P(321.0,191.0) , P(322.0,198.0) , P(322.0,211.0) , P(323.0,226.0) , P(324.0,229.0) , P(324.0,238.0) , P(324.0,263.0) , P(325.0,272.0) , P(325.0,281.0) , P(325.0,288.0) , P(325.0,291.0) , P(325.0,297.0) , P(325.0,299.0) , P(325.0,301.0) , P(325.0,305.0) , P(324.0,306.0) , P(324.0,307.0) , P(323.0,308.0) , P(324.0,307.0) , P(325.0,307.0) , P(328.0,306.0) , P(332.0,306.0) , P(339.0,306.0) , P(347.0,305.0) , P(354.0,304.0) , P(365.0,304.0) , P(376.0,304.0) , P(379.0,304.0) , P(385.0,304.0) , P(391.0,304.0) , P(392.0,304.0) , P(393.0,304.0) , P(393.0,302.0) , P(393.0,301.0) , P(394.0,297.0) , P(394.0,290.0) , P(393.0,284.0) , P(393.0,274.0) , P(392.0,258.0) , P(391.0,245.0) , P(391.0,233.0) , P(389.0,213.0) , P(388.0,198.0) , P(388.0,189.0) , P(388.0,184.0) , P(388.0,178.0) , P(388.0,177.0) , P(388.0,176.0) , P(388.0,174.0)
.................................................................................................................. .................................................................................  , P(388.0,173.0) , P(388.0,171.0) , P(388.0,170.0) , P(388.0,168.0) , P(388.0,167.0) , P(388.0,166.0) , P(388.0,165.0) , P(389.0,165.0) , P(390.0,165.0) , P(395.0,165.0) , P(401.0,165.0) , P(406.0,165.0) , P(418.0,166.0) , P(424.0,167.0) , P(426.0,167.0) , P(429.0,167.0) , P(430.0,167.0) , P(431.0,167.0) , P(432.0,167.0) , P(433.0,169.0) , P(434.0,170.0) , P(434.0,174.0) , P(436.0,185.0) , P(440.0,200.0) , P(442.0,220.0) , P(442.0,224.0) , P(446.0,267.0) , P(447.0,279.0) , P(448.0,286.0) , P(448.0,287.0) , P(448.0,287.0)]

 Bonding box is  = Corner P(195.0, 162.0), w= 253.0, h=  146.0
 \end{scriptsize}
  \\ \hline
  & Possible Dominate point Extraction for details see Section\ref{sec:Preprocessing} &  Stroke points  & 1. compute the $P_{pd}$  & \begin{scriptsize}   Number of $P_{pd}$  =  36

 Pdp = [ 25 (195.0 , 278.0 ), 30 (195.0 , 285.0 ), 33 (195.0 , 295.0 ), 27 (195.0 , 281.0 ), 34 (195.0 , 297.0 ), 46 (213.0 , 301.0 ), 47 (217.0 , 302.0 ), 50 (234.0 , 304.0 ), 28 (195.0 , 282.0 ), 94 (260.0 , 174.0 ), 93 (260.0 , 176.0 ), 95 (260.0 , 173.0 ), 98 (260.0 , 169.0 ), 48 (219.0 , 302.0 ), 99 (260.0 , 168.0 ), 109 (275.0 , 162.0 ), 113 (301.0 , 163.0 ), 94 (260.0 , 174.0 ), 132 (325.0 , 272.0 ), 136 (325.0 , 297.0 ), 112 (291.0 , 162.0 ), 137 (325.0 , 299.0 ), 110 (279.0 , 162.0 ), 144 (325.0 , 307.0 ), 147 (339.0 , 306.0 ), 150 (365.0 , 304.0 ), 132 (325.0 , 272.0 ), 168 (388.0 , 189.0 ), 171 (388.0 , 177.0 ), 174 (388.0 , 173.0 ), 146 (332.0 , 306.0 ), 175 (388.0 , 171.0 ), 183 (395.0 , 165.0 ), 186 (418.0 , 166.0 ), 169 (388.0 , 184.0 ), 191 (431.0 , 167.0 ) ]

  \end{scriptsize}
    \\ \hline
 \\ \hline 
Segmentation & Segmentation of Ellipse & $P_{dp}$   &  Ellipse fitting  & 
  The Ellipse is   a = 125.5 ,b = 125.5 , Center( 320.5,  235.0 )   with Error =  7.074966523515405 , Percent =1.1481777694994926 certainty  =  0.08114368920921669  
 \\ \hline
 Segmentation & PSO Segmentation ALgS1 & $P_{dp}$  & ALgS1 &   Particles =  [  1 0 1 0 0 1 1 1 1 1 1 0 0 0 1 0 0 0 1 ] 
 The particle  Particles =  [  1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 1 0 0 0 0 1 0 ]

 First Polygonization PSO = [[[  S0 Line[P(201.0,179.0) to P(195.0,281.0)]  ,      S1 Line[P(195.0,281.0) to P(234.0,304.0)]  ,      S2 Line[P(234.0,304.0) to P(260.0,174.0)]  ,      S3 Line[P(260.0,174.0) to P(325.0,272.0)]  ,      S4 Line[P(325.0,272.0) to P(365.0,304.0)]  ,      S5 Line[P(365.0,304.0) to P(388.0,189.0)]  ,      S6 Line[P(388.0,189.0) to P(431.0,167.0)]  ,      S7 Line[P(431.0,167.0) to P(442.0,220.0)]  ]]]  
 \\ \hline

		\end{longtable}
%}

%\end{table}

\end{scriptsize}

\end{landscape}

%\begin{enumerate}
%\begin{itemize}

%	\item Processing for the first Stroke 1.

%	\item Possible Dominiate Point Extraction
%	\item Segmentation 
%	   Computing 
%	\begin{enumerate}
%	\item Ellipse detection  
%	      Calcualting estimated ellipse with radius = $\frac{w}{2}$  and center as same as the bounding box of stroke.  
%	      The ouput of the system $$
% \end{enumerate}
%	
%	
%\end{enumerate}
%  
%
%\end{itemize}
